---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# rankgradute

<!-- badges: start -->
<!-- badges: end -->

The goal of `rankgraduate` is to provide basic and easy-to-understand information on the rank of major colleges in the United States with Shiny Application. Moreover, this package provides the dataset of the rank of graduates in the USA and the basic functions that users can use.

## Installation

You can install the development version of rankgraduate from [GitHub](https://github.com/etc5523-2022/rpkg-aphiaut) with:

``` r
# install.packages("devtools")
devtools::install_github("etc5523-2022/rpkg-aphiaut")
```


## Get Started

```{r, message=FALSE, warning=FALSE}
library(rankgraduate)
```


```{r, eval=FALSE}
# Launch shiny application
launch_app()
```


## An example of function

```{r}
rankgraduate::employee("Nursing")
```

```{r}
rankgraduate::table_rank(100000,40000)
```

## Learn More About the Package and Functions

Refer to the [pkgdown
website](https://rankgraduate.netlify.app/)
