---
title: "Rank Graduate Package"
author: "Aphiaut Imuan"
format: 
  revealjs:
    theme: moon
editor: visual
---

## Rank Graduate Package

The package include ranking of the 2018 graduate in USA. When users run this package, they will be able to use 4 functions

-   Launch shiny application

-   Illustrate how each degree fits into job requirement using graph

-   Find maximum and minimum of each variables

-   Show the table of the top 6 median income

    ```{r}
    #| echo: false
    library(tidyverse)
    ```

## Install the package

<br>

```{r}
#| echo: true
#| eval: false
# install.packages("devtools")
devtools::install_github("etc5523-2022/rpkg-aphiaut")
library(rankgraduate)

```

## Launch shiny application

<br>

```{r}
#| echo: true
#| eval: false

rankgraduate::run_app()
```

## Graph Illustration

The graph illustrates how different industries require various majors from university such as Nurses role prefer graduate that has the nursing degree.

```{r}
#| echo: true
rankgraduate::employee("Nursing")
```

## Numeric Function

Function shows the maximum and minimum for each elements for example median income and number of graduate.

<br>

`maxvar()` and `minvar()` are created as it is easy and straightforward for beginner users to access the data.

## Examples of Numeric Function

<br>

```{r}
#| echo: true
#| eval: true

rankgraduate::maxvar("Unemployed")

```

```{r}
#| echo: true
#| eval: true

rankgraduate::minvar("Unemployed")
```

<br>

This function shows that there are maximum of 28169 graduate that are unemployed in the certain degree on the other hand, another degree has minimum unemployment is 0.

## Top 6 Median Income Table

The table showcases the median income level for top 6 majors in the university.

<br>

The users will be able to understand the certain degree in deeper level and to choose ranges of the data depending on their preference.

## Example of table function 

```{r}
#| echo: true
#| eval: true

rankgraduate::table_rank(100000,40000) %>%
  kableExtra::kable() %>%
  kableExtra::kable_styling(full_width = F)
```
