---
title: "Rank Graduated Package"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Rank Graduated Package}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```


# Getting Started

The `rankgraduate` package serves as a container for a Shiny Application. This vignette describes how do you launch the application, download the dataset, and use basic function from this package.

## Install and read the package

```{r, message=FALSE}
#devtools::install_github("etc5523-2022/rpkg-aphiaut")
library(rankgraduate)
```


## Launching the Shiny Application

```{r launch-app, eval = FALSE}
launch_app()
```

## Download the dataset

```{r dataset, eval = FALSE}
rankgraduate::university
```

This dataset behind the story [The Economic Guide To Picking A College Major](https://fivethirtyeight.com/features/the-economic-guide-to-picking-a-college-major/). If you want to know the variables of this dataset, you can use a single line of code:

```{r, eval = FALSE}
?rankgraduate::university
```




## The basic functions

```{r, eval = FALSE}
rankgraduate::max("The numeric variable that you interested")
rankgraduate::min("The numeric variable that you interested")
```

These functions can illustrate the maximum and minimum of the numeric variable without dataset and $ in the line code.

## The graph employee function

```{r, eval=FALSE}
rankgraduate::employee("The name of major that you interested")
```

This function illustrates the figure of the number of jobs that require the major degree in the USA. If you don't sure about the name of major, you can use a single line of code:

```{r, eval=FALSE}
unique(rankgraduate::university$Major)
```


